The imprint of global magma oceans on exoplanet demographics

### 2022-08-22 src/tex/ms.tex
prepare acknowledgements
add example corner plot, caption

@@

@@

\begin{note}
    \textit{Here or in the introduction:} For observations of rocky exoplents, the currently best-probed regime is hot, close-in planets.
    These bodies experience climatic conditions that are similar to the environment of the inner Solar System bodies at early stages of their formation.
    Studies of the geophysical state and evolution of hot exoplanets can thus contribute to our understanding of the early formation stages of Earth and other habitable worlds.
\end{note}

>>>>

\subsection{Signature and testability of the magma ocean hypothesis with a $<nominal telescope size>$ class space telescope survey}

\begin{figure}[ht!]
%    \script{figurescript.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/example_cornerplot.pdf}
        \caption{
        Retrieved posterior distribution of magma ocean model. The density maps in each panel show relationships between and marginalized distributions of the model parameters as they would be retrieved with a targeted $<nominal telescope size>$ survey of $<survey duration>$ duration. True values of the injected magma ocean parameters are shown in orange. ...
        }
        \label{fig:cornerplot}
    \end{centering}
\end{figure}

@@

\subsection{Atmospheric signatures}
\todo[inline]{discuss potential atmospheric signatures of magma oceans. e.g.: H/O ratios of sub-Neptunes could be low (because H is in the melt) (Tim's talk)}

@@

\begin{note}
    \textit{Here or in the introduction:} For observations of rocky exoplanets, the currently best-probed regime that of hot, close-in planets.
    These bodies experience climatic conditions that are similar to the environment of the inner Solar System bodies at early stages of their formation.
    Studies of the geophysical state and evolution of hot exoplanets can thus contribute to our understanding of the early formation stages of Earth and other habitable worlds.
\end{note}

%\begin{acknowledgments}
%The authors thank Terry-Ann Suer for insightful discussions.
%\end{acknowledgements}
